PyPy's Approach to Virtual Machine Construction

### 2006-05-31 talk/dls2006/paper.tex
two small tweaks motivated by line lengths.

Of course, this would be pointless if the annotation did not give
precise enough information for our needs.  We must describe a detail of
the abstract interpretation engine that is critical for precision: the
propagation of conditional types.  Consider the following source code
fragment:
%
\begin{verbatim}
    if isinstance(x, MyClass):
        f(x)
    else:
        g(x)
\end{verbatim}
%
Although the type of \texttt{x} may be some parent class of
\texttt{MyClass}, it can be deduced to be of the more precise type
$Inst(MyClass)$ within the positive branch of the
\texttt{if}.\footnote{Remember that our graphs are in SSI form,
which means that the
\texttt{x} inside each basic block is a different Variable with a
possibly different type as annotation.  Given that our type inference
is not flow-sensitive, SSI gives an advantage over SSA here.}

@@

As described in section \ref{experimentalresults}, the performance of
the compiled Python interpreters is still not up to competing with the
well-established CPython.  We are always working to improve matters,
considering new optimizations and better GCs.  Also, the OOTyper and
back-ends for Smalltalk/Squeak and CLI/.NET are currently in progress.

>>>>

Of course, this would be pointless if the annotation did not give
precise enough information for our needs.  We must describe a detail of
the abstract interpretation engine that is critical for precision: the
propagation of conditional types.  Consider the following source code
fragment:
%
\begin{verbatim}
    if isinstance(x, MyClass):
        f(x)
    else:
        g(x)
\end{verbatim}
%
Although the type of \texttt{x} may be some parent class of
\texttt{MyClass}, within the positive branch of the \texttt{if} it can
be deduced to be of the more precise type $Inst(MyClass)$.\footnote{Remember
 that our graphs are in SSI form, which means
that the \texttt{x} inside each basic block is a different Variable
with a possibly different type as annotation.  Given that our type
inference is not flow-sensitive, SSI gives an advantage over SSA
here.}

@@

As described in section \ref{experimentalresults}, the performance of
the compiled Python interpreters is still not up to competing with the
well-established CPython.  We are always working to improve matters,
considering new optimizations and better GCs.  Also, the OOTyper and
back-ends for CLI/.NET and Smalltalk/Squeak are currently in progress.
